sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields

### 2022-01-14 doc/paper.Rmd
Tweak headers; remove marked

<!-- # Introductory example with fish survey biomass -->
# Introductory example using fish survey data

@@

<!-- # Spatially varying coefficient example with citizen science data -->
# 2. Estimate a spatially varying effect from citizen science data

@@

We found a weak average positive effect of annual mean NAO on overall counts, but a marked southeast to northwest gradient in the intensity of the effect (Fig. \@ref(fig:owl-nao), Appendix 3).
This result is consistent with owls closest to the Atlantic coast and those migrating the furthest south being the most affected by NAO.

>>>>

# Introductory example using fish survey data

@@

# Example of a spatially varying coefficient with citizen science data
<!-- # Estimate a spatially varying effect from citizen science data -->

@@

We found a weak average positive effect of annual mean NAO on overall counts, but a southeast to northwest gradient in the intensity of the effect (Fig. \@ref(fig:owl-nao), Appendix 3).
This result is consistent with owls closest to the Atlantic coast and those migrating the furthest south being the most affected by NAO.
